R5R

### 2020-08-22 r-package/tests_marcus/tests r5r.Rmd
Fixed detailed_itineraries function return when drop_geometry = TRUE

paths_df <- detailed_itineraries(r5r_core = r5r_core, origins = origin, destinations = destination, 
                     departure_datetime = trip_date_time, max_walk_dist = 0.8, 
                     mode = c("WALK", "BICYCLE", "BUS"),
                     shortest_path = FALSE, verbose = FALSE)

@@

>>>>

paths_df <- detailed_itineraries(r5r_core = r5r_core, origins = origin, destinations = destination, 
                     departure_datetime = trip_date_time, max_walk_dist = 0.8, 
                     mode = c("WALK", "BICYCLE", "BUS"),
                     shortest_path = FALSE, verbose = FALSE, drop_geometry = FALSE)

@@

```{r}
paths_df
```
